### 2016-07-31 Doc/MSelection/mselection.tex
review printout

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
%\rfoot{\thepage/\pageref{lastpage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Continuous evolution of bacteriophage has the potential to become a potent protein engineering tool\cite{pace}\cite{monsanto}.
For example, PACE - Phage Assisted Continuous Evolution described by Esvelt,Carlson and Lui. 
Continuous evolution rapidly produces a viral genome containing a gene
which has undergone many generations of mutation and selection for
a particular property.  The generality of this approach to protein engineering
is limited by our ability to insert an expressable initial gene into the phage and create a selection mechanism for the desired activity.

@@

\item{}
A modified viral genome replacing a crucial phage gene with a gene to be evolved.

@@

\section{M-Selection}
Extremely high, yet controllable, in-vivo mutation rates are now possible\cite{mutation}.  This mutagenesis can be generated and controlled within an individual host cell.  I suggest that if this mutagenesis is initiated  by infection, say with the phage shock promotor but then reduced by the desired activity, the two principal components of evolution will be satisfied and the desired activity will be selected for as the number of phage progeny of the individual exhibiting that activity will be amplfied by proportionally more faithful reproduction.  I propose calling this mechanism Mutagenesis-selection or M-selection.

High rates of mutation will be associated with little or none of the desired activity, and these lines of descent (both E. coli and phage) will be subject to catastrophic levels of mutation and low viability.

@@

A possible drawback to this technique is that the mutation space is less agressively searched as the desired activity improves.  But there is no particular reason that the modulation of mutation rate necessary to produce the population shift will be a low (e.g. natural) mutation rate.

\section{Possible Benefits of M-Selection}
\begin{enumerate}
\item{The virus is not crippled, that is, no critical genes need to be removed from the virion which will improve our ability to propagate phage prior to the evolution experiment.  Of course, as usual, care must be taken to ensure that the evolving gene is not discarded before the experiment begins.  However, M13 with one additional gene(domain) is exactly what has been perfected in phage display.}
\item{No phage genes are required in a host plasmid.  This avoids the problem associated with the presence of gIII in the host.}
\end{enumerate}

@@

\put(35,90){\boxtwo{\ Phage Shock}{\ \ \ Promoter}}
\put(-20,55){
\fbox{%
    \begin{minipage}{1.0in}
Activity Induced\linebreak
\hspace*{5 mm}Repressor
    \end{minipage}%
}}
\put(64,60){\vector(1,0){18}}
\put(83,57){\fbox{\begin{minipage}{0.05in}
		\hfill\vspace{0.30in}
            \end{minipage}
           }}
\put(35,0){\boxtwo{MUTAGENESIS\ }{\ \ \ Components}}

\put(130,15){\vector(1,0){30}}
\put(180,15){\circleone{40}{\Large{\ \ F1}}}

@@

\subsection*{Population Dyamics of Bacteriophage}
\subsubsection*{Clones versus Mutants}
Although it may sounds like the title of a recent movie, this precisely states the selection mechanism of of mutation.

Percentage of activated genes due to Phage Shock promoter.
Number of polIII-(mutagenic polymerase) transcripts times error rate due to mutagenic polymerase.
Error rate of normal polII, polIII

Number of phage particles produced np(0-6 min) = 0 (six minutes before any phage appears), then production between 75-200 per hour.

Some initial single-strand (virion) DNA production will occur in non-mutagenic environment, then mutants appear, until suppression of mutagenesis due to binding(desired activity).

>>>>

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
%\rfoot{\thepage/\pageref{lastpage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
%\lfoot{\sf PLOS}
\lfoot{\sf NCMLS}

@@

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Continuous evolution of bacteriophage has the potential to become a potent protein engineering tool\cite{pace}\cite{monsanto}.
Continuous evolution rapidly produces a viral genome containing a gene
which has undergone many generations of mutation and selection for
a particular property.  The generality of this approach to protein engineering
is limited by our ability to insert an expressable initial gene into the phage and create a selection mechanism for the desired activity.

@@

\item{}
A modified viral genome replacing a crucial phage gene with the gene to be evolved.

@@

\section{M-Selection}
Extremely high, yet controllable, in-vivo mutation rates are now possible\cite{mutation}.  This mutagenesis can be generated and controlled within an individual host cell.  I suggest that if this mutagenesis is initiated  by infection, say with the phage shock promotor but then reduced by the desired activity, the two principal components of evolution will be satisfied: the desired activity will be selected for as the number of phage progeny of the individual exhibiting that activity will be amplfied by more faithful reproduction.  I propose calling this mechanism Mutagenesis-selection or M-selection.

@@

A possible drawback to this technique is that the mutation space is less agressively searched as the desired activity improves.  But there is no particular reason that the modulation of mutation rate necessary to produce the population shift will be a particularly low (e.g. natural) mutation rate.

\section{Possible Benefits of M-Selection}
\begin{enumerate}
\item{The virus is not crippled, that is, no critical genes need to be removed from the virion which will improve our ability to propagate phage prior to the evolution experiment.  Of course, as usual, care must be taken to ensure that the evolving gene is not discarded before the experiment begins.  However, M13 with one additional gene(domain) is exactly what has been perfected in phage display.}
\item{No phage genes are required in a host plasmid.  This avoids the problem associated with the presence of gIII in the host.}
\item{High rates of mutation will be associated with individuals exhibiting little or none of the desired activity, and these lines of descent (both E. coli and phage) will be subject to catastrophic levels of mutation and low viability. This may reduce the importance of a carefully controlled flow rate.}
\end{enumerate}

@@

\put(35,90){\boxtwo{\ Phage Shock}{\ \ \ Promoter}}
\put(-20,55){
\fbox{%
    \begin{minipage}{1.0in}
Activity Induced\linebreak
\hspace*{5 mm}Repressor
    \end{minipage}%
}}
\put(64,60){\vector(1,0){18}}
\put(83,57){\fbox{\begin{minipage}{0.05in}
		\hfill\vspace{0.30in}
            \end{minipage}
           }}
\put(35,0){\boxtwo{MUTAGENIC}{\ \ Components}}

\put(134,15){\vector(1,0){26}}
\put(180,15){\circleone{40}{\Large{\ \ F1}}}

@@

\subsection*{Population Dyamics of Bacteriophage (Under Constuction)}
\subsubsection*{Clones versus Mutants}
Although it may sounds like the title of a bad sci-fi movie, this precisely states the selection mechanism of of mutation.
\newline
Percentage of activated genes due to Phage Shock promoter.
\newline
Number of polIII-(mutagenic polymerase) transcripts times error rate due to mutagenic polymerase.
\newline
Error rate of normal polII, polIII?
\newline
Number of phage particles produced np(0-6 min) = 0 (six minutes before any phage appears), then production between 75-200 per hour.
\newline
Some initial single-strand (virion) DNA production will occur in non-mutagenic environment, then mutants appear, until suppression of mutagenesis due to binding(desired activity).
